%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
\cventry
{Infrastructure Devops Analyst} % Job title
{Fundunesp} % Organization
{Remoto} % Location
{2022 - now} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {SRE/DevOps teamwork experience}
    \item {Support to development squads}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {DevOps Senior Analyst} % Job title
    {Havan} % Organization
    {Remote} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {SRE/DevOps teamwork experience}
        \item {Support to development squads}
        \item {Observability activities mainly using DataDog, creating dashboards, alerts}
        \item {CI/CD Pipelines - Jenkins, AzureDevops, Harness}
        \item {Delivery automations in legacy environments - Windows Server}
        \item {Kubernetes Administration - Rancher and Openshift}
        \item {Application containerization}
        \item {Support in cloud environment administration - Azure DevOps}
        \item {Repository Management - Azure DevOps, Git, TFVC}
        \item {Automations with Python, Groovy, Shell script, Ansible and PowerShell}
        \item {Work on creating and maintaining automated quality tests and code patterns at Sonarqube}
        \item {Automated Security Tests (SAST/DAST) with HCL}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Infrastructure Administrator - Servers, Networks and Systems} % Job title
    {UNESP - Universidade Estadual Paulista} % Organization
    {Presidente Prudente, SP} % Location
    {2009 - 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Several network services administration and deployment (DNS, DHCP, Web Servers - Apache, NGINX, Tomcat, pfSense, IPAM, Zabbix, Nagios...)}
        \item {Server virtualization experience (VMware, Xen, KVM) - including the entire infrastructure migration from VMware hypervisor to Xen}
        \item {Services and applications containerization experience (Docker, Docker-compose, Portainer) - several services migration from VMs to containers}
        \item {Network infrastructure management (switches, routers, access points)}
        \item {Equipment and services monitoring (Zabbix, Grafana, Prometheus)}
        \item {Python, Shell script, Ansible automation}
        \item {Some experience in management, acting as IT Director Substitute.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Computer Technician - development and Infrastructure manager} % Job title
    {Colégio Braga Mello} % Organization
    {Presidente Prudente, SP} % Location
    {2008 - 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Academic, Financial and Payroll Control Systems development.}
        \item {Linux and Windows Server servers deployment and administration.}
        \item {Databases administration (MySQL, PostgreSQL)}
      \end{cvitems}
    }


%---------------------------------------------------------
\cventry
{Trainee - development} % Job title
{MTTEC - Automação Industrial} % Organization
{Presidente Prudente, SP} % Location
{2007 - 2008} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Participation in the development team of ERP projects, Commercial Automation, TEF (Electronic Fund Transfer), among others. Primarily using Visual Basic and PostgreSQL databases. ASP.Net, Java and PHP experience.}
  \end{cvitems}
}


%---------------------------------------------------------
\cventry
{Trainee - development} % Job title
{Global Automação} % Organization
{Presidente Prudente, SP} % Location
{2003 - 2007} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Working on development project team for Commercial Automation, Gas Station Management System, among others. Working with Visual Basic and MySQL databases.}
  \end{cvitems}
}


%---------------------------------------------------------
\cventry
{Trainee} % Job title
{Agência Brasileira de Correios e Telégrafos} % Organization
{Presidente Prudente, SP} % Location
{2003 - 2003} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Computers and network maintenance. Database implementation for company internal use.}
  \end{cvitems}
}


%---------------------------------------------------------
\cventry
{Trainee} % Job title
{Yázigi - Escola de Idiomas} % Organization
{Presidente Prudente, SP} % Location
{2001 - 2002} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Network, systems, machines and website maintenance. And Computer Lab supervision.}
  \end{cvitems}
}


\end{cventries}
