%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Free time project} % Affiliation/role
{cTwittLike (web and iOS App)} % Organization/group
{Google AppEngine, Python, Swift, App Store} % Location
{2009 - 2014} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Application with the objective of see Twitter like someone else.}
    \item {First developed in Python and run on Google AppEngine.}
    \item {Covered by \href{https://mashable.com/archive/ctwitterlike}{Mashable}, \href{https://www.engadget.com/2014-10-08-view-someone-elses-own-twitter-timeline-with-ctwittlike.html}{Engadget}, Tecnoblog, among others, causing great traffic in which I had to work on project scale to meet the requests.}
    \item {Years later the idea was developed in Swift and made available as an iOS app.}      
  \end{cvitems}
}


%---------------------------------------------------------
\cventry
{Free time project} % Affiliation/role
{Reminder Widget: for Evernote Reminders (iOS app)} % Organization/group
{Objective-C} % Location
{2015} % Date(s)
{
\begin{cvitems} % Description(s) of experience/contributions/knowledge
  \item {iOS Application created to supply the lack of a widget (better than the official one at the time) for Evernote reminders.}
  \item {Developed right on the release of iOS widget development.}
  \item {Details on \href{https://appadvice.com/app/reminder-widget-for-evernote-reminders/1000192150}{AppAdvice}.}
\end{cvitems}
}


%---------------------------------------------------------
  \cventry
    {Free time project} % Affiliation/role
    {Ganhei? (iOS app)} % Organization/group
    {Swift, Node.js, AWS, App Store} % Location
    {2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Application to register games and check results of Mega-Sena (brazilian lottery).}
        \item {Project developed in Swift with backend in Node.js to send notifications when the result of the draw is released.}
        \item {OCR use to recognize numbers played when reading bet ticket for automatic registration.}
        \item {Covered by \href{https://macmagazine.com.br/post/2017/06/14/com-o-app-ganhei-voce-cadastra-seus-jogos-da-mega-sena-com-uma-foto-e-sabe-se-ficou-milionario-em-primeira-mao/}{MacMagazine} as application suggestion.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
